\documentclass[10pt,letterpaper]{article}

\usepackage[top=0.58in,bottom=0.58in,left=0.62in,right=0.62in]{geometry}
\usepackage[
  colorlinks=true,
  urlcolor=ink,
  linkcolor=ink
]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{array}

\definecolor{ink}{HTML}{172033}
\definecolor{muted}{HTML}{526070}
\definecolor{rule}{HTML}{D8DEE6}
\definecolor{accent}{HTML}{184E77}
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0pt}
\setlength{\parskip}{0pt}
\setlength{\emergencystretch}{2em}
\renewcommand{\familydefault}{\sfdefault}
\setlist[itemize]{
  leftmargin=1.2em,
  topsep=2pt,
  itemsep=1.5pt,
  parsep=0pt,
  label=\textcolor{accent}{\small\textbullet}
}
\titleformat{\section}
  {\normalsize\bfseries\color{accent}}
  {}
  {0pt}
  {}
  [\vspace{-2pt}{\color{rule}\titlerule}]
\titlespacing*{\section}{0pt}{8pt}{4pt}

\newcommand{\resumeHeader}[6]{
  \begin{center}
    {\fontsize{22}{24}\selectfont\bfseries\color{ink} #1}\\[-1pt]
    {\normalsize\bfseries\color{accent} Software Engineer}\\[4pt]
    {\small\color{muted} #2 \quad | \quad #3 \quad | \quad \href{mailto:#4}{#4}}\\[-1pt]
    {\small\color{muted} \href{#5}{linkedin.com/in/avinash-mallick} \quad | \quad \href{#6}{github.com/avimallick}}
  \end{center}
  \vspace{-4pt}
}

\newcommand{\role}[4]{
  \vspace{2pt}
  {\bfseries\color{ink} #1} \hfill {\small\color{muted} #2}\\
  {\itshape\color{muted} #3} \hfill {\small\itshape\color{muted} #4}
}

\newcommand{\project}[3]{
  \vspace{2pt}
  {\bfseries\color{ink} #1} \hfill {\small\color{muted} #2}\\
  {\itshape\color{muted} #3}
}

\newcommand{\summary}[1]{
  \begingroup
  \color{ink}
  \linespread{1.03}\selectfont
  #1
  \endgroup
}

\newcommand{\skillrow}[2]{
  \begingroup
  \raggedright
  {\bfseries\color{ink}#1:} #2\par\vspace{2pt}
  \endgroup
}

\begin{document}

\resumeHeader
  {Avinash Mallick}
  {London, UK}
  {(+44) 07741014524}
  {avimallick@gmail.com}
  {https://www.linkedin.com/in/avinash-mallick-b272b6214/}
  {https://github.com/avimallick}

\section*{Software Engineer}
\summary{Software engineer with a focus on AI integration and deployment. I work closely with product teams to translate business requirements into scalable, maintainable solutions. My experience includes developing full-stack applications, implementing CI/CD pipelines, and optimizing performance across various technologies.}

\section*{Technical Skills}
\skillrow{Languages}{Python, TypeScript, JavaScript, C\#, Java, SQL}
\skillrow{AI Engineering}{LangGraph, LangChain, LlamaIndex, DSPy, RAG, agentic workflows, embeddings, vector search, LLM evaluation, Langfuse, context engineering}
\skillrow{Backend \& Infra}{FastAPI, Pydantic, PostgreSQL, pgvector, Redis, Docker, Caddy, AWS EC2, Cloudflare Pages, GitHub Actions}
\skillrow{Enterprise}{React, Angular, .NET Core, ASP.NET, Entity Framework, Azure Cloud, IBM Cloud, v-net peering}

\section*{Experience}
\role{Post Urban Ventures}{Oct 2025 -- Present}{AI Systems Engineer - Consultant}{London, UK}
\begin{itemize}
  \item Worked directly with founders and product teams to identify operational bottlenecks, scope AI workflows, and ship production-ready prototypes across venture-backed products including Chelo.ai and VFree.
  \item Built modular AI microservices using FastAPI, Python, LangGraph, PostgreSQL, pgvector, Redis, and Docker, enabling rapid deployment of LLM-powered workflows into startup environments.
  \item Embedded with insurance brokers to map an unstructured, WhatsApp-based claims workflow, then scoped and shipped a human-in-the-loop agent routing policy questions through retrieval and agent verification (Twilio, production observability) --- keeping a broker approval gate on every customer-facing reply.
  \item Developed RAG pipelines, knowledge graph integrations, and backend orchestration patterns for customer-facing AI products deployed on AWS, Cloudflare, and self-hosted infrastructure.
\end{itemize}

\role{Converso}{Nov 2025 -- Present}{AI Engineer}{London, UK}
\begin{itemize}
  \item Designed and deployed LangGraph-based conversational agents for CRM automation, integrating structured ingestion, retrieval, and customer-specific knowledge workflows for enterprise datasets.
  \item Deployed a self-hosted Langfuse observability stack, adding tracing, structured logs, latency monitoring, and evaluation workflows to debug and improve agent reliability in production.
  \item Built document processing and RAG pipelines using embeddings, vector search, validation layers, and human-review patterns to improve trust in AI-generated customer support workflows.
  \item Partnered with product and engineering stakeholders to translate ambiguous automation requirements into scoped, shipped AI features with monitoring and rollout considerations.
\end{itemize}

\role{IBM}{June 2025 -- Sep 2025}{Software Engineer, Contract - Joint UCL-IBM Collaboration}{London, UK}
\begin{itemize}
  \item Built an agentic code modernization system for Java codebases, using RAG, LangGraph, FastAPI, Pydantic, and IBM Granite models to detect anti-patterns, propose refactors, and generate explainable code changes.
  \item Designed a multi-agent workflow with scanner, refactor strategist, code transformer, reviewer, and explainer agents, adding compile/test gating to improve reliability of AI-generated refactors.
  \item Evaluated the system on 10,000+ lines of Java code, achieving 85\% anti-pattern detection precision and reducing manual modernization effort by an estimated 60\%.
\end{itemize}

\newpage
\role{Eurofins Scientific - Eurofins IT Delivery Centre}{June 2023 -- Sep 2024}{Associate Software Engineer}{Bangalore, India}
\begin{itemize}
  \item Delivered full-stack eCommerce solutions handling 25,000+ monthly transactions, improving checkout conversion rates by 12\% through optimized UI/UX implementations using C\#, ASP.NET, and SQL.
  \item Spearheaded Azure cloud segregation initiative serving 15,000+ users across 8 global regions, reducing deployment time by 45\% and infrastructure costs by \pounds30,000 annually.
  \item Engineered cross-tenant networking solutions using Azure v-net peering, enabling secure data flow for 200+ microservices with 99.8\% reliability.
\end{itemize}

\section*{Selected AI Engineering Work}
\project{Agentic COBOL to Python Migration}{Langflow, Python, Semi-Formal Verification, LLMs}{Legacy modernization agent}
\begin{itemize}
  \item Created AI-powered code migration framework achieving 78\% automated conversion accuracy on legacy COBOL systems containing 50,000+ lines of code.
  \item Won DataStax Hacking Agents Hackathon ``Best Use Case of Langflow'' among 150+ participants from across Europe.
\end{itemize}

\project{TopoIndex Python Library}{Python, RDKit, NetworkX, Poetry, PyPI, GitHub Actions}{Molecular analysis package}
\begin{itemize}
  \item Built and published an open-source molecular-analysis library (PyPI, CI via GitHub Actions) for QSAR feature extraction, designed for batch processing of large compound sets in cheminformatics pipelines.
  \item Implemented validated topological-index algorithms against published reference values, with vectorized graph traversal running \textasciitilde55\% faster than a naïve NetworkX baseline on 1,000+ compound batches.
\end{itemize}

\section*{Achievements}
\begin{itemize}
  \item \textbf{Oxford Enspire Guest Lecturer:} Delivered lecture on AI-assisted coding, spec-driven development, and practical AI prototyping for founders at Christ Church College, University of Oxford.
  \item \textbf{Google DeepMind $\times$ Cactus Compute Hackathon - 2nd Prize:} Built hybrid local/cloud agentic AI system for privacy-sensitive workflows.
  \item \textbf{AI Tooling in SDLC - Best Use Case of ACI.dev:} Built AI anti-pattern remediation tool using local LLMs, MCP, and GitHub codebase interaction.
\end{itemize}

\section*{Education}
\textbf{University College London} \hfill Sept 2024 -- Sept 2025\\
\textit{Master of Science, Software Systems Engineering} \hfill London, UK\\
{\small\color{muted}\textbf{Grade:} Merit \textbar{} \textbf{Coursework:} Engineering of Data Analysis, Applied Deep Learning, Software Development Practices}

\vspace{2pt}
\textbf{Hindustan Institute of Technology and Science} \hfill July 2019 -- April 2023\\
\textit{Bachelor of Technology (Honours), Computer Science and Engineering} \hfill Chennai, India\\
{\small\color{muted}\textbf{Coursework:} Data Structures, Algorithms, Machine Learning, Cloud Computing, Compiler Theory, Distributed Systems}

\end{document}